---
title: "immunaut"
author: "Ivan Tomic <info@ivantomic.com>"
output: github_document
vignette: >
  %VignetteIndexEntry{immunaut}
  %VignetteEngine{knitr::rmarkdown}
  usepackage[utf8]{inputenc}
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
R package designed to facilitate machine learning analysis with multi-dimensional datasets. The codebase provides functions to perform dimensionality reduction, hierarchical clustering, and predictive modeling. Within this framework, users can use high-dimensional data, perform t-distributed stochastic neighbor embedding (t-SNE) for effective visualization and exploration, and then carry out hierarchical clustering to identify latent data structures. This analysis chain can then be extended by further appending the data with cluster results, allowing for the construction of machine learning models with specific outcomes. The package is well-suited for exploratory data analysis, enabling users to uncover patterns, dynamics, and structures within their complex datasets.

## Installation

You can install the released version of **immunaut** from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("immunaut")
```
Or you can install **immunaut** directly from **GitHub** with use of following commands:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("atomiclaboratory/immunaut", subdir = 'R-package')
```

## Usage Example
```{r example-setup, eval = TRUE}
library("immunaut")

## Using provided demo data
data(immunautDemo)

settings <- list()
settings$fileHeader <- generate_file_header(immunautDemo)

#results <- immunaut(immunautDemo, settings)

```
## Example 1
```{r example-1, message=FALSE, warning=FALSE}


```
